### 2021-12-21 paper/manuscript.Rmd
comments/additions paper

abstract: |
  When analyzing a heterogeneous body of literature, there may be many
  potentially relevant between-studies differences. These differences can be
  coded as moderators, and accounted for using meta-regression. However, many
  applied meta-analyses lack the power to adequately account for multiple
  moderators, as the number of studies on any given topic is often low. The
  present study introduces Bayesian Regularized Meta-Analysis (BRMA), an
  exploratory algorithm that can select relevant moderators from a larger number
  of candidates. This approach is suitable when heterogeneity is suspected, but
  it is not known which moderators most strongly inﬂuence the observed effect
  size. We present a simulation study to validate the performance of BRMA
  relative to state-of-the-art meta-regression (RMA). Results indicated that
  BRMA compared favorably to RMA on three metrics: predictive performance,
  which is a measure of the generalizability of results, the ability to reject
  irrelevant moderators, and the ability to recover population parameters with
  low bias. BRMA had slightly lower ability to detect true effects of relevant
  moderators, but the overall proportion of Type I and Type II errors was
  equivalent to RMA. Furthermore, BRMA regression coefficients were slightly
  biased towards zero (by design), but its estimates of residual heterogeneity
  were unbiased. BRMA performed well with as few as 20 studies in the training
  data, suggesting its suitability as a small sample solution. We discuss how
  applied researchers can use BRMA to explorate between-studies heterogeneity
  in meta-analysis.

keywords          : "meta-analysis, machine learning, bayesian, lasso, regularized"
wordcount         : "5356"

@@

It is theoretically possible to account for the influence of multiple moderators using meta-regression.
However, like any regression-based approach, meta-regression requires a relatively high number of cases (studies) per parameter obtain sufficient power to examine heterogeneity.
In practice the number of available studies is often too low to examine heterogeneity reliably (Riley, Higgins, & Deeks, 2011).
At the same time, there are many potential sources of heterogeneity,
as similar research questions are studied in different laboratories, using different methods,
instruments, and samples.
This leads to a problem known as the "curse of dimensionality": the number of candidate moderators is large relative to the number of cases in the data.
Such cases do not fit comfortably into the
classic meta-analysis paradigm, which, like any regression-based approach, requires a
high number of cases per parameter. 
Between-studies thus presents a non-trivial challenge to data aggregation
using classic meta-analytic methods.
At the same time, it also offers an unexploited
opportunity to learn which differences between studies have an impact on the effect size
found, if adequate exploratory techniques can be developed.

Addressing the curse of dimensionality necessitates *variable selection*:
the selection of a smaller subset of relevant moderators from a larger number of candidate moderators.
One way to perform variable selection is by relying on theory.
However, in many fields of science, theories exist at the individual level of analysis (e.g., in social science, at the level of individual people).
These theories do not necessarily generalize to the study level of analysis.
Using theories at the individual level for moderator selection at the study level amounts to committing the ecological fallacy: generalizing inferences across levels of analysis [@jargowskyEcologicalFallacy2004].
To illustrate what theory at the study level of analysis might look like, 
consider the so-called *decline effect*.
It is a phenomenon whereby effect sizes in a particular tranche of the literature seem to diminish over time [@schoolerUnpublishedResultsHide2011].
It has been theorized that the decline effect can been attributed to regression to the mean:
A finding initially draws attention from the research community because an anomalously large effect size has been published, and subsequent replications find smaller effect sizes.
Based on the decline effect, we might thus expect the variable "year of publication" to be a relevant moderator of study effect sizes.
Note that this prediction is valid even if year is orthogonal to the outcome of interest within each study.
Until more theory about the drivers of between-study heterogeneity is developed,
however, this approach will have limited utility for variable selection.
<!--A second example that might illustrate this problem is a study that concluded that American college students' empathy had decreased over time, based on meta-analysis of 72 samples collected between 1979 and 2009.-->

@@

Under the fixed effect model, the estimated population effect size  $\hat{\theta}$ is obtained by computing a weighted average of the observed effect sizes.
If sampling error is assumed to be the only source of variance in observed effect size,
then it follows that studies with smaller standard errors estimate the underlying true effect size more precisely<!--(Schmidt, Oh \& Hayes, 2009)-->.
The fixed-effect weights are thus simply the reciprocal of the sampling variance, $w_{i} =  \frac{1}{v_i}$.
The estimate of the true effect is a weighted average across observed effect sizes:

@@

If the true effect sizes follow a distribution, 
then even less precise studies (with larger sampling errors) may provide some information about this distribution.
Like fixed-effect weights, random effects weights are still influenced by sampling error, but this influence is attenuated by the estimated variance of the true effect sizes. 
The random-effects weights are thus given by $w_{i} =  \frac{1}{v_i + \hat{\tau}^2}$.
It is important to note that,
whereas the sampling error for each individual effect size is treated as known,
between-study heterogeneity $\tau^{2}$ must be estimated.
This estimate is represented by $\hat{\tau}^{2}$.

@@

The random effects model assumes that causes of heterogeneity in the true effect sizes are unknown, and that their influence is random.
Oftentimes, however, there are systematic sources of heterogeneity in true effect sizes.
These between-study differences can be coded as moderators, and their influence can be estimated and controlled for using meta-regression.
Meta-regression with $p$ moderators can be expressed with the following equation, where $x_{1\ldots p}$ represent the moderators, and $\beta_{1\ldots p}$ the regression coefficients:

@@

In contrast to a regularized analysis technique, this estimator produces low bias, which means that the average value of the estimated regression coefficients and residual heterogeneity is close to their true values (Panityakul et al., 2013; Hardy & Thompson, 1996).

@@

$$
RSS=\sum_{i=1}^{n}(y_{i} - \beta_{0} - \sum_{j=1}^{p}\beta_{j}x_{ij})^2
$$
The resulting parameter estimates are those that give the best predictions of the dependent variable in the present dataset.
Penalized regression, by contrast, adds a penalty term to the quantity to be minimized.
One commonly used penalty is the L1-norm of the regression coefficients, or LASSO penalty,
which corresponds to the sum of their absolute values.
This gives the penalized residual sum of squares:

@@

Where $\lambda$ is a tuning parameter that determines how influential the penalty term will be.
If $\lambda$ is zero, the shrinkage penalty has no impact at all and the penalized regression will produce the OLS estimates.
If $\lambda \to \infty$, all coefficient shrink towards zero, producing the null model.
<!--Another commonly used penalty is the L2-norm of the coefficients, or ridge penalty,
which corresponds to the sum of their squared values: $\sum_{j=1}^{p}\beta_{j}^2$.-->
Because the penalty term is a function of the regression coefficients,
the optimizer has an incentive to keep the regression coefficients as small as possible.
<!--The LASSO penalty has the unique property of shrinking some coefficients to be exactly zero,
but the ridge penalty does not do so, as -->
Note that theLASSO penalty is but one example of a shrinkage penalty; other penalties exist, with some unique properties.

@@

@@

The present study set out to validate the BRMA algorithm using a simulation study.
As a benchmark for comparison, we used restricted maximum likelihood meta-regression,
which is the standard in the field.
We evaluated the algorithms' predictive performance in new data, 
<!-- examining its predictive performance in new data, its sensitivity and specificity in variable selection, and its bias and variance in recovering population parameters. -->
<!-- their ability to perform variable selection, -->
and their ability to recover population parameters. 
Our research questions are whether BRMA offers a performance advantage over RMA in terms of any of these indicators;
under what conditions BRMA does not offer an advantage,
and which prior (horseshoe versus LASSO) is to be preferred.

@@

Predictive performance reflects how well the algorithm is able to predict data not used to estimate the model parameters, in other words, it indicates the generalizability of the model.
To compute it, for each iteration of the simulation both a training dataset and a testing dataset are generated.
The model is estimated on the training data, which has a varying number of cases according to the simulation conditions.
Predictive performance is then operationalized as the explained variance in the testing data, $R^2_{test}$.
The testing data has 100 cases in all simulation conditions.
The $R^2_{test}$ reflects the fraction of variance in the testing data explained by the model,
relative to the variance explained by the mean of the training data.
For a predictive performance measure, it is necessary to use the mean of the training data, as the mean of the testing is a descriptive statistic of that sample.
The resulting metric $R_{test}^{2}$ is expressed by the following equation:

$$
R_{cv}^{2} = 1- \frac{\sum_{i=1}^{k}(y_{i-test}-\hat{y}_{i-test})^{2}}{\sum_{i=1}^{k}(y_{i-test}-\bar{y}_{train})^{2}}
$$

@@

To examine performance in a range of realistic meta-analysis scenarios,
several design factors were manipulated:
The number of studies in the training data $k \in (20, 40, 100)$, the average within-study sample size $\bar{n} \in (40, 80, 160)$, the population effect size of relevant moderators $\beta \in (0, .2, .5, .8)$, the number of moderators $p \in (2, 3, 6)$, and residual heterogeneity $\tau^{2} \in (.01, .04, .1)$.
According to a review of 705 published psychological meta-analyses (Van Erp et al., 2017),
these values of $\tau^2$ fall within the range observed in practice.
Note that both BRMA and RMA assume linear effects.
To test the robustness of the algorithms to violations of this assumption, true effect sizes were simulated using two models:
one with a linear effect of one moderator, $T_{i}= \beta x_{1i} + \epsilon_i$, and one with a non-linear (cubic) effect of one moderator, $T_{i}= \beta x_{1i} + \beta x_{1i}^{2} + \beta x_{1i}^{3} + \epsilon_i$,
where $\epsilon_i \sim N(0, \tau^2)$.
The algorithms further assume normality of residuals.
To examine robustness of the algorithms to violations of this assumption,
moderator variables were simulated as skewed normal moderators, with scale parameter $\omega \in (0, 2, 10)$, where $\omega = 0$ corresponds to the standard normal distribution.
The design factors combined to produce `r out$conditions` unique conditions.
For all simulation conditions, 100 data sets were generated. 
In each data set, the observed effect size $y_i$ was simulated as a standardized mean difference (SMD),
sampled from a non-central t-distribution.

@@

The RMA algorithm failed to converge for `r out$missing` replications, all of which were characterized by low number of cases ($k \leq 40$) and high effect sizes $\beta \geq .5$.
These cases were omitted from further analysis.

@@

Within data sets, the BRMA with a horseshoe prior had the highest predictive performance `r round(whichhi[1]*100)`% of the time, followed by RMA, `r round(whichhi[3]*100)`%, and finally BRMA with a LASSO prior, `r round(whichhi[2]*100)`%.
Results indicated that the overall $R^2_{test}$ was highest for BRMA with a Horseshoe prior and lowest for RMA, see \@ref(tab:tabr2).
This difference was driven in part by the fact that explained variance was somewhat higher for the BRMA models when the true effect was not null, and by the fact that RMA had larger negative explained variance when the true effect was equal to zero (i.e., there was no effect to detect).

@@

To test our research questions, we computed interactions of algorithm (HS vs. LASSO, HS vs. RMA and LASSO vs. RMA) with the other design factors.
The $\eta^2$ of these differences between algorithms are also displayed in Table \@ref(tab:tabr2eta).
Note that $\eta^2$ for the comparison between HS and LASSO was zero in the second decimal for all conditions; thus, this comparison was omitted from the Table.
The effect of design factors by algorithm is displayed in Figure \@ref(fig:figr2); these plots have been ranked from largest difference between BRMA and RMA to smallest.
Results indicate that the largest differences between algorithms were due to the effect size $\beta$, number of irrelevant moderators $M$, and the number of cases in the training data $k$.
Evidently, predictive performance increased most for the HS algorithm when the effect size increased above zero.
As noted previously, predictive performance of RMA was most negative (negative explained variance) when the effect size was zero.
The HS algorithm furthermore had the consistently highest predictive performance regardless of number of irrelevant moderators or number of cases in the training data, and was relatively less affected by increases in the number of irrelevant moderators (panel b) or in the number of training cases (panel c).
Similarly, the HS algorithm furthermore had the consistently highest predictive performance regardless of number of cases in the training data, and thus also increased less when the number of training cases increased (panel c).
Conversely, RMA had relatively poor predictive performance on average, and was more responsive to increases in the number of training cases and irrelevant moderators.

@@

The effect of the design factors on the bias in estimated $\beta$ was evaluated using ANOVAs.
Table \@ref(tab:tabbeta) reports the effect size $\eta^{2}$ of simulation conditions on $\hat{b}-\beta$.
The skewness of moderator variables had the largest effect on bias in estimated $\beta$ for all algorithms.
Note, however, that this is likely due to the fact that the data simulated with a cubic model are analyzed with a linear model, and thus,  
was the estimated model. This was mainly because the algorithms overestimated $\tau^{2}$ most when the model contained cubic terms.
No differences between algorithms in the effect of design factors were observed.

@@

Results indicated that the BRMA algorithms had higher predictive performance than RMA in the presence of relevant moderators.
In the absence of relevant moderators, RMA produced overfit models; in other words, its models generalized poorly to new data.
The predictive performance of the BRMA algorithms also suffered less than that of RMA in the presence of more irrelevant moderators.
The BRMA algorithms were also more efficient, in the sense that they achieved greater predictive performance when the number of studies in the training data was low.
Across all conditions, BRMA with a horseshoe prior achieved the highest average predictive performance, and within each data set, BRMA with a horseshoe prior most often had the best predictive performance (in `r round(whichhi[1]*100)`% of replications).
This provides strong evidence that BRMA with a horseshoe prior is generally preferable when the goal is to obtain findings that generalize to new data.

@@

Several limitations remain to be addressed in future research, however.
One limitation is that, by necessity, computational resources and journal space limit the number of conditions that could be considered in the simulation study.
To facilitate further exploration and follow-up research,
we have made all simulation data and analysis code for the present study available online.
This code also enables researchers to conduct Monte Carlo power analyses for applied research.
Another limitation is that the present study did not examine the effect of multicolinear predictors.
Regularizing estimators typically have an advantage over OLS regression in the presence of multicolinearity;
future research ought to examine whether this also applies to BRMA.

@@

Alghough the use of Bayesian estimation has several advantages, one major downside is that Bayesian models are not directly comparable with frequentist models.
Another disadvantage is that Bayesian estimation is typically more computationally expensive than frequentist estimation.
One future direction of research is thus to develop a frequentist estimator for regularized meta-regression.

>>>>

abstract: |
  When analyzing a heterogeneous body of literature, there may be many
  potentially relevant between-studies differences. These differences can be
  coded as moderators, and accounted for using meta-regression. However, many
  applied meta-analyses lack the power to adequately account for multiple
  moderators, as the number of studies on any given topic is often low. The
  present study introduces Bayesian Regularized Meta-Analysis (BRMA), an
  exploratory algorithm that can select relevant moderators from a larger number
  of candidates. This approach is suitable when heterogeneity is suspected, but
  it is not known which moderators most strongly inﬂuence the observed effect
  size. We present a simulation study to validate the performance of BRMA
  relative to state-of-the-art meta-regression (RMA). Results indicated that
  BRMA compared favorably to RMA on three metrics: predictive performance,
  which is a measure of the generalizability of results, the ability to reject
  irrelevant moderators, and the ability to recover population parameters with
  low bias. BRMA had slightly lower ability to detect true effects of relevant
  moderators, but the overall proportion of Type I and Type II errors was
  equivalent to RMA. Furthermore, BRMA regression coefficients were slightly
  biased towards zero (by design), but its estimates of residual heterogeneity
  were unbiased. BRMA performed well with as few as 20 studies in the training
  data, suggesting its suitability as a small sample solution. We discuss how
  applied researchers can use BRMA to explore between-studies heterogeneity
  in meta-analysis.

keywords          : "meta-analysis, machine learning, bayesian, lasso, horseshoe, regularized"
wordcount         : "5356"

@@

It is theoretically possible to account for the influence of multiple moderators using meta-regression.
However, like any regression-based approach, meta-regression requires a relatively high number of cases (studies) per parameter to obtain sufficient power to examine heterogeneity.
In practice the number of available studies is often too low to examine heterogeneity reliably (Riley, Higgins, & Deeks, 2011).
At the same time, there are many potential sources of heterogeneity,
as similar research questions are studied in different laboratories, using different methods,
instruments, and samples.
This leads to a problem known as the "curse of dimensionality": the number of candidate moderators is large relative to the number of cases in the data.
Between-studies differences thus present a non-trivial challenge to data aggregation
using classic meta-analytic methods.
At the same time, it also offers an unexploited
opportunity to learn which differences between studies have an impact on the effect size
found, if adequate exploratory techniques can be developed.

Addressing the curse of dimensionality necessitates *variable selection*:
the selection of a smaller subset of relevant moderators from a larger number of candidate moderators.
One way to perform variable selection is by relying on theory.
However, in many fields of science, theories exist at the individual level of analysis (e.g., in social science, at the level of individual people).
These theories do not necessarily generalize to the study level of analysis.
Using theories at the individual level for moderator selection at the study level amounts to committing the ecological fallacy: generalizing inferences across levels of analysis [@jargowskyEcologicalFallacy2004].
To illustrate what a theory at the study level of analysis might look like, 
consider the so-called *decline effect*.
It is a phenomenon whereby effect sizes in a particular tranche of the literature seem to diminish over time [@schoolerUnpublishedResultsHide2011].
It has been theorized that the decline effect can be attributed to regression to the mean:
A finding initially draws attention from the research community because an anomalously large effect size has been published, and subsequent replications find smaller effect sizes.
Based on the decline effect, we might thus expect the variable "year of publication" to be a relevant moderator of study effect sizes.
Note that this prediction is valid even if year is orthogonal to the outcome of interest within each study.
Until more theory about the drivers of between-study heterogeneity is developed,
however, this approach will have limited utility for variable selection.
<!--A second example that might illustrate this problem is a study that concluded that American college students' empathy had decreased over time, based on meta-analysis of 72 samples collected between 1979 and 2009.-->

@@

Under the fixed effect model, the estimated population effect size  $\hat{\theta}$ is obtained by computing a weighted average of the observed effect sizes.
If sampling error is assumed to be the only source of variance in the observed effect size,
then it follows that studies with smaller standard errors estimate the underlying true effect size more precisely<!--(Schmidt, Oh \& Hayes, 2009)-->.
The fixed-effect weights are thus simply the reciprocal of the sampling variance, $w_{i} =  \frac{1}{v_i}$.
The estimate of the true effect is a weighted average across observed effect sizes:

@@

If the true effect sizes follow a distribution, 
then even less precise studies (with larger sampling errors) may provide some information about this distribution.
Like fixed-effect weights, random effects weights are still influenced by sampling error, but this influence is attenuated by the estimated variance of the true effect sizes. 
The random-effects weights are thus given by $w_{i} =  \frac{1}{v_i + \hat{\tau}^2}$.
It is important to note that,
whereas the sampling error for each individual effect size is treated as known, the
between-study heterogeneity $\tau^{2}$ must be estimated.
This estimate is represented by $\hat{\tau}^{2}$.

@@

The random-effects model assumes that causes of heterogeneity in the true effect sizes are unknown, and that their influence is random.
Oftentimes, however, there are systematic sources of heterogeneity in true effect sizes.
These between-study differences can be coded as moderators, and their influence can be estimated and controlled for using meta-regression.
Meta-regression with $p$ moderators can be expressed with the following equation, where $x_{1\ldots p}$ represent the moderators, and $\beta_{1\ldots p}$ the regression coefficients:

@@

In contrast to a regularized analysis technique, this estimator produces low bias, which means that the average value of the estimated regression coefficients and residual heterogeneity is close to their true values (Panityakul et al., 2013; Hardy & Thompson, 1996). However, due to the bias-variance tradeoff, this bias comes at the cost of high variance, meaning that the results might not generalize to a new sample. Regularization can offer a solution to this problem.

@@

$$
RSS=\sum_{i=1}^{n}(y_{i} - \beta_{0} - \sum_{j=1}^{p}\beta_{j}x_{ij})^2
$$
The resulting parameter estimates are those that give the best predictions of the dependent variable in the present dataset.
Penalized regression, by contrast, adds a penalty term to the RSS.
One commonly used penalty is the L1-norm of the regression coefficients, or LASSO penalty (Tibshirani, 1996),
which corresponds to the sum of their absolute values.
This gives the penalized residual sum of squares:

@@

Where $\lambda$ is a tuning parameter that determines how influential the penalty term will be.
If $\lambda$ is zero, the shrinkage penalty has no impact at all and the penalized regression will produce the OLS estimates.
If $\lambda \to \infty$, all coefficients shrink towards zero, producing the null model.
<!--Another commonly used penalty is the L2-norm of the coefficients, or ridge penalty,
which corresponds to the sum of their squared values: $\sum_{j=1}^{p}\beta_{j}^2$.-->
Generally, cross-validation is used to find the optimal value for the penalty parameter $\lambda$.
<!--The LASSO penalty has the unique property of shrinking some coefficients to be exactly zero,
but the ridge penalty does not do so, as -->
Note that the LASSO penalty is but one example of a shrinkage penalty; other penalties exist.

@@

Instead of using a penalty to shrink regression coefficients towards zero, it is possible to use a Bayesian prior distribution to achieve a similar result. Whereas classical, frequentist estimation methods rely solely on the data at hand, Bayesian estimation methods require the specification of a prior distribution. The prior distribution is a probability distribution that reflects the prior knowledge or beliefs that the researcher has before collecting the data. The prior is combined with the likelihood of the data to form the posterior distribution. In the context of regularization, the prior distribution is specified such that it reflects the prior belief that not all regression coefficients are substantial enough to be included in the model.

Many different prior distributions exist that have specific properties that enable them to shrink small regression coefficients towards zero, while keeping substantial coefficients large (van Erp, Oberski & Mulder, 2019). Some prior distributions have been shown to result in exactly the same solutions as classical, frequentist penalties, such as the LASSO. Specifically, placing independent Laplace (i.e., double exponential) priors on the regression coefficients results in posterior modes that are equal to the lasso estimates (Park and Casella, 2008). In addition, many prior distributions have been developed and investigated specifically for the purpose of providing good shrinkage properties, meaning that the prior pulls small regression coefficients towards zero, without exerting any influence on substantial regression coefficients. A popular prior in this regard is the horseshoe prior (Carvalho et al. 2010). An advantage of the horseshoe prior compared to the lasso is the fact that it has heavier tails. As a result, it will not shrink and therefore bias substantial coefficients as much as the LASSO prior with its lighter tails.

### Implementation
The brma function uses Stan (Stan development team) to fit the models. Stan is a probabilistic programming language that uses a Hamiltonian Monte Carlo algorithm to sample from the posterior distribution. When running a Bayesian analysis in Stan it is important to ensure that the algorithm has converged to the posterior distribution in order for the results to be trusted. Stan offers automatic warnings and errors if this might not be the case.

Currently, the brma function supports two priors: the LASSO and the regularized horseshoe. We have precompiled the models with these two priors using brms (brms ref).

The LASSO prior is implemented as follows:

$$
\beta_{j} \sim \text{double exponential}(0, \frac{s}{lambda})
$$

and requires the specification of a global scale parameter $s$ and an inverse-tuning parameter $\lambda$. By default, the global scale is set to 1 and the inverse-tuning parameter is given a chi-square prior with degrees of freedom equal to 1.

For the horseshoe prior, we use an extension proposed by Piironen and Vehtari (2017) called the regularized horseshoe:

$$
\beta_{j} \sim \text{normal}(0, \tilde{\tau}_j^2\lambda) \text{, with } \tilde{\tau}_j^2 = \frac{c^2 \tau_j^2}{c^2 + \lambda^2 \tau_j^2} \\
\lambda \sim \text{half-t}(\nu_1, 0, \lambda^2_0) \\
\tau_j \sim \text{half-t}(\nu_2, 0, 1) \\
c^2 \sim \text{inverse-gamma}(\frac{\nu_3}{2}, \frac{\nu_3 s^2}{2})
$$

This extension is more numerically stable in certain cases. In addition, it allows the user to explicitly include prior information regarding the number of relevant moderators by setting the argument par_ratio to the ratio of the expected number of non-zero coefficients to the expected number of zero coefficients. If this information is not available, the user should specify scale_global ($\lambda^2_0$) which affects the overall shrinkage of the prior, with smaller values resulting in more shrinkage (default = 1). In addition, the regularized horseshoe has two degrees of freedom parameters ($\nu_1$ and $\nu_2$) which default to 1. Increasing the degrees of freedom parameters results in a prior with lighter tails, which is strictly no longer a horseshoe prior. However, the lighter tails might be needed in certain cases to attain convergence. 
The regularized horseshoe differs from the horseshoe in the specification of a finite "slab". This ensures at least some regularization of large coefficients and as a consequence, more stable results. This slab is governed by a degrees of freedom parameter ($\nu_3$, set to 4) and a scale parameter ($s$, set to 1).

We have chosen all default settings for the hyperparameters such that the values are reasonable in most applications. However, in a Bayesian analysis it is good practice to perform a prior sensitivity analysis in which different hyperparameters are chosen and the model is rerun to see if this leads to different results.

Unlike the classical frequentist lasso, Bayesian regularized estimation cannot estimate coefficients to be exactly equal to zero. Therefore, some approach is needed to select variables post-estimation. the brma funciton currently uses credible intervals (the Bayesian counterpart of confidence intervals) to do so, with a moderator being selected if the 95% credible interval excludes zero.

@@

The present study set out to validate the BRMA algorithm using a simulation study.
As a benchmark for comparison, we used restricted maximum likelihood meta-regression,
which is the standard in the field.
We evaluated the algorithms' predictive performance in new data, 
<!-- examining its predictive performance in new data, its sensitivity and specificity in variable selection, and its bias and variance in recovering population parameters. -->
<!-- their ability to perform variable selection, -->
and their ability to recover population parameters. 
Our research questions are whether BRMA offers a performance advantage over RMA in terms of any of these indicators;
under what conditions BRMA does not offer an advantage,
and which prior (regularized horseshoe versus LASSO) is to be preferred.

@@

Predictive performance reflects how well the algorithm is able to predict data not used to estimate the model parameters, in other words, it indicates the generalizability of the model.
To compute it, for each iteration of the simulation both a training dataset and a testing dataset are generated.
The model is estimated on the training data, which has a varying number of cases according to the simulation conditions.
Predictive performance is then operationalized as the explained variance in the testing data, $R^2_{test}$.
The testing data has 100 cases in all simulation conditions.
The $R^2_{test}$ reflects the fraction of variance in the testing data explained by the model,
relative to the variance explained by the mean of the training data.
For a predictive performance measure, it is necessary to use the mean of the training data, as the mean of the testing set is a descriptive statistic of that sample. **ik vind deze zin niet heel duidelijk**
The resulting metric $R_{test}^{2}$ is expressed by the following equation:

$$
R_{test}^{2} = 1- \frac{\sum_{i=1}^{k}(y_{i-test}-\hat{y}_{i-test})^{2}}{\sum_{i=1}^{k}(y_{i-test}-\bar{y}_{train})^{2}}
$$

@@

To examine performance in a range of realistic meta-analysis scenarios,
several design factors were manipulated:
The number of studies in the training data $k \in (20, 40, 100)$, the average within-study sample size $\bar{n} \in (40, 80, 160)$, the population effect size of relevant moderators $\beta \in (0, .2, .5, .8)$, the number of moderators $p \in (2, 3, 6)$, and residual heterogeneity $\tau^{2} \in (.01, .04, .1)$. **het aantal moderatoren is redelijk laag; ik zou vooral nog voordelen van brma verwachten met meer moderatoren maar is dat realistisch in de praktijk? Zo ja, dan is het iets om te noemen in de discussie**
According to a review of 705 published psychological meta-analyses (Van Erp et al., 2017),
these values of $\tau^2$ fall within the range observed in practice.
Note that both BRMA and RMA assume linear effects.
To test the robustness of the algorithms to violations of this assumption, true effect sizes were simulated using two models:
one with a linear effect of one moderator, $T_{i}= \beta x_{1i} + \epsilon_i$, and one with a non-linear (cubic) effect of one moderator, $T_{i}= \beta x_{1i} + \beta x_{1i}^{2} + \beta x_{1i}^{3} + \epsilon_i$,
where $\epsilon_i \sim N(0, \tau^2)$.
The algorithms further assume normality of residuals.
To examine robustness of the algorithms to violations of this assumption,
moderator variables were simulated as skewed normal moderators, with scale parameter $\omega \in (0, 2, 10)$, where $\omega = 0$ corresponds to the standard normal distribution.
The design factors combined to produce `r out$conditions` unique conditions.
For all simulation conditions, 100 data sets were generated. 
In each data set, the observed effect size $y_i$ was simulated as a standardized mean difference (SMD),
sampled from a non-central t-distribution.

@@

The RMA algorithm failed to converge for `r out$missing` replications, all of which were characterized by low number of cases ($k \leq 40$) and high effect sizes $\beta \geq .5$.
These cases were omitted from further analysis.
**was er volledige convergence voor brma in alle replicaties? Dat heb ik zelf namelijk nog nooit meegemaakt.**

@@

Within data sets, the BRMA with a horseshoe prior had the highest predictive performance `r round(whichhi[1]*100)`% of the time, followed by RMA, `r round(whichhi[3]*100)`%, and finally BRMA with a LASSO prior, `r round(whichhi[2]*100)`%.
Results indicated that the overall $R^2_{test}$ was highest for BRMA with a horseshoe prior and lowest for RMA, see \@ref(tab:tabr2).
This difference was driven in part by the fact that explained variance was somewhat higher for the BRMA models when the true effect was not null **moet zijn null?**, and by the fact that RMA had larger negative explained variance when the true effect was equal to zero **moet zijn not equal to zero?** (i.e., there was no effect to detect).**deze statements lijken niet overeen te komen met de tabel**

@@

To test our research questions, we computed interactions of algorithm (HS vs. LASSO, HS vs. RMA and LASSO vs. RMA) with the other design factors.
The $\eta^2$ of these differences between algorithms are also displayed in Table \@ref(tab:tabr2eta).
Note that $\eta^2$ for the comparison between HS and LASSO was zero in the second decimal for all conditions; thus, this comparison was omitted from the Table.
The effect of design factors by algorithm is displayed in Figure \@ref(fig:figr2); these plots have been ranked from largest difference between BRMA and RMA to smallest.
Results indicate that the largest differences between algorithms were due to the effect size $\beta$, number of irrelevant moderators $M$, and the number of cases in the training data $k$.
Evidently, predictive performance increased most for the HS algorithm when the effect size increased above zero.
As noted previously, predictive performance of RMA was most negative (negative explained variance) when the effect size was zero.
The HS algorithm furthermore had the consistently highest predictive performance regardless of number of irrelevant moderators or number of cases in the training data, and was relatively less affected by increases in the number of irrelevant moderators (panel b) or in the number of training cases (panel c).
Similarly, the HS algorithm furthermore had the consistently highest predictive performance regardless of number of cases in the training data, and thus also increased less when the number of training cases increased (panel c).
Conversely, RMA had relatively poor predictive performance on average, and was more responsive to increases in the number of training cases and irrelevant moderators. However, differences between the algorithms were generally small.

@@

The effect of the design factors on the bias in estimated $\beta$ was evaluated using ANOVAs.
Table \@ref(tab:tabbeta) reports the effect size $\eta^{2}$ of simulation conditions on $\hat{b}-\beta$.
The skewness of moderator variables had the largest effect on bias in estimated $\beta$ for all algorithms.
Note, however, that this is likely due to the fact that the data simulated with a cubic model are analyzed with a linear model, and thus,  
was the estimated model. **met brma zouden we de kwadratische en kubieke termen mee kunnen nemen en penalizen in het model. Misschien noemen als optie?** This was mainly because the algorithms overestimated $\tau^{2}$ most when the model contained cubic terms.
No differences between algorithms in the effect of design factors were observed.

@@

Results indicated that the BRMA algorithms had higher predictive performance than RMA in the presence of relevant moderators.
In the absence of relevant moderators, RMA produced overfit models; in other words, its models generalized poorly to new data.
The predictive performance of the BRMA algorithms also suffered less than that of RMA in the presence of more irrelevant moderators.
The BRMA algorithms were also more efficient, in the sense that they achieved greater predictive performance when the number of studies in the training data was low.
Across all conditions, BRMA with a horseshoe prior achieved the highest average predictive performance, and within each data set, BRMA with a horseshoe prior most often had the best predictive performance (in `r round(whichhi[1]*100)`% of replications).
This provides strong evidence that BRMA with a horseshoe prior is generally preferable when the goal is to obtain findings that generalize to new data. **In mijn ogen waren de verschillen in performance niet heel groot, dus ik vraag me af of het nu niet iets te sterk is opgeschreven. Maar jij bent meer bezig geweest met de simulatie, dus mogelijk zie ik iets over het hoofd.**

@@

Several limitations remain to be addressed in future research, however.
One limitation is that, by necessity, computational resources and journal space limit the number of conditions that could be considered in the simulation study.
To facilitate further exploration and follow-up research,
we have made all simulation data and analysis code for the present study available online.
This code also enables researchers to conduct Monte Carlo power analyses for applied research.
Another limitation is that the present study did not examine the effect of multicollinear predictors.
Regularizing estimators typically have an advantage over OLS regression in the presence of multicollinearity;
future research ought to examine whether this also applies to BRMA.

@@

Alghough the use of Bayesian estimation has several advantages, one major downside is that Bayesian models are not directly comparable with frequentist models.
Another disadvantage is that Bayesian estimation is typically more computationally expensive than frequentist estimation.
One future direction of research is thus to develop a frequentist estimator for regularized meta-regression.
Additionally, the current implementation relies on 95% credible intervals to select relevant moderators. However, these marginal credible intervals can behave differently compared to the joint credible intervals (Piironen, Betancourt, Simpson & Vehtari, 2017). A second future direction of research is therefore to implement more advanced selection procedures, such as projection predictive variable selection (Piironen & Vehtari, 2016).
